---
title: "TidyTemplate"
date: 2022-08-03
output: html_document
---

# TidyTuesday - frogs

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(lubridate)

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2022-08-02")

frogs <- tt$frogs
```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}
frogs %>% 
  glimpse()

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

frogs <- frogs %>% 
  mutate(SurveyDate = mdy(SurveyDate),
         Ordinal = as.numeric(Ordinal), 
         Frequency = as.numeric(Frequency),
         UTME_83 = as.numeric(UTME_83),
         UTMN_83 = as.numeric(UTMN_83),
         Interval = as.numeric(Interval),
         Female = as.numeric(Female)) %>% 
  mutate_if(is.character, as.factor)
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

frogs %>% 
  group_by(Female) %>% 
  summarise(Frequency = sum(Frequency)) %>% 
  ggplot(aes(Female, Frequency)) +
  geom_col()
  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
